---
title: "Pricing Model for Airbnb"
author: "Maxime Boelen, Alexander Loer, Eva Nijssen & Yuhu Wang"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

## Setup

We will use the following packages in this notebook:
```{r message = FALSE}
library("tidymodels")
library("tidyverse")
library("readr")
library("stringr")
```

# Data Ingestion and Cleaning

## Loading the Data

```{r include=FALSE}
col_spec <- cols(
  id = col_integer(),
  listing_url = col_character(),
  scrape_id = col_double(),
  last_scraped = col_date(),
  name = col_character(),
  summary = col_character(),
  space = col_character(),
  description = col_character(),
  experiences_offered = col_character(),
  neighborhood_overview = col_character(),
  notes = col_character(),
  transit = col_character(),
  access = col_character(),
  interaction = col_character(),
  house_rules = col_character(),
  thumbnail_url = col_character(),
  medium_url = col_character(),
  picture_url = col_character(),
  xl_picture_url = col_character(),
  host_id = col_integer(),
  host_url = col_character(),
  host_name = col_character(),
  host_since = col_character(),
  host_location = col_character(),
  host_about = col_character(),
  host_response_time = col_factor(levels = c("within an hour", "within a few hours", "within a day", "a few days or more", "N/A")),
  host_response_rate = col_character(),
  host_acceptance_rate = col_character(), # only contains N/A
  host_is_superhost = col_factor(levels = c("t", "f")),
  host_thumbnail_url = col_character(),
  host_picture_url = col_character(),
  host_neighbourhood = col_character(),
  host_listings_count = col_integer(),
  host_total_listings_count = col_integer(),
  host_verifications = col_character(),
  host_has_profile_pic = col_factor(levels = c("t", "f")),
  host_identity_verified = col_factor(levels = c("t", "f")),
  street = col_character(),
  neighbourhood = col_character(),
  neighbourhood_cleansed = col_character(),
  neighbourhood_group_cleansed = col_character(),
  city = col_character(),
  state = col_character(),
  zipcode = col_character(),
  market = col_factor(levels = c("Amsterdam", "Barcelona", "Other (International)", "Vilnius")),
  smart_location = col_character(),
  country_code = col_character(),
  country = col_character(),
  latitude = col_character(),
  longitude = col_character(),
  is_location_exact = col_factor(levels = c("t", "f")),
  property_type = col_character(),  # could be transformed to factor
  room_type = col_factor(levels = c("Private room", "Entire home/apt", "Hotel room", "Shared room")),
  accommodates = col_double(),
  bathrooms = col_double(),
  bedrooms = col_integer(),
  beds = col_integer(),
  bed_type = col_factor(levels = c("Real Bed", "Airbed", "Couch", "Futon", "Pull-out Sofa")),
  amenities = col_character(),
  square_feet = col_double(),
  price = col_number(),
  weekly_price = col_number(),
  monthly_price = col_number(),
  security_deposit = col_number(),
  cleaning_fee = col_number(),
  guests_included = col_integer(),
  extra_people = col_number(),
  minimum_nights = col_integer(),
  maximum_nights = col_integer(),
  minimum_minimum_nights = col_integer(),
  maximum_minimum_nights = col_integer(),
  minimum_maximum_nights = col_integer(),
  maximum_maximum_nights = col_integer(),
  minimum_nights_avg_ntm = col_double(),
  maximum_nights_avg_ntm = col_double(),
  calendar_updated = col_character(),
  has_availability  = col_factor(levels = c("t", "f")), # has only true values
  availability_30 = col_integer(),
  availability_60 = col_integer(),
  availability_90 = col_integer(),
  availability_365 = col_integer(),
  calendar_last_scraped = col_date(),
  number_of_reviews = col_integer(),
  number_of_reviews_ltm = col_integer(),
  first_review = col_date(),
  last_review = col_date(),
  review_scores_rating = col_integer(),
  review_scores_accuracy = col_integer(),
  review_scores_cleanliness = col_integer(),
  review_scores_checkin = col_integer(),
  review_scores_communication = col_integer(),
  review_scores_location = col_integer(),
  review_scores_value = col_integer(),
  requires_license  = col_factor(levels = c("t", "f")), # has only false values
  license = col_character(), # empty
  jurisdiction_names = col_character(),
  instant_bookable  = col_factor(levels = c("t", "f")),
  is_business_travel_ready  = col_factor(levels = c("t", "f")), # has only false values
  cancellation_policy = col_factor(levels = c("strict_14_with_grace_period", "moderate", "flexible", "super_strict_30", "super_strict_60")),
  require_guest_profile_picture = col_factor(levels = c("t", "f")),
  require_guest_phone_verification = col_factor(levels = c("t", "f")),
  calculated_host_listings_count = col_integer(),
  calculated_host_listings_count_entire_homes = col_integer(),
  calculated_host_listings_count_private_rooms = col_integer(),
  calculated_host_listings_count_shared_rooms = col_integer(),
  reviews_per_month = col_double()
)

df_listings <- read_csv("listings.csv", 
                  col_names = TRUE, col_types = col_spec, na = c("N/A", ""))
```

## Create Subset with Relevant Variables

```{r}
df_listings <- df_listings %>% select(id, summary, host_since, host_location, host_response_time, host_response_rate, host_is_superhost, host_listings_count, host_total_listings_count, host_verifications, host_has_profile_pic, host_identity_verified, latitude, longitude, is_location_exact, property_type, room_type, accommodates, bathrooms, bedrooms, beds, bed_type, amenities, price, security_deposit, cleaning_fee, guests_included, extra_people, minimum_nights, maximum_nights, minimum_minimum_nights, maximum_minimum_nights, minimum_maximum_nights, maximum_maximum_nights, minimum_nights_avg_ntm, maximum_nights_avg_ntm, availability_30, availability_60, availability_90, availability_365, requires_license, instant_bookable, is_business_travel_ready, cancellation_policy, require_guest_profile_picture, require_guest_phone_verification, calculated_host_listings_count, calculated_host_listings_count_entire_homes, calculated_host_listings_count_private_rooms, calculated_host_listings_count_shared_rooms)
```

Reasons why vars are not included:

no entries: experiences: , medium_url, host_acceptance_rate
only true values: has_availability
not available at start: number_of_reviews
too many missing values: square feet

## Clean Variables
```{r}
# Extract Numerical Variables
df_listings <- df_listings %>%
  mutate(host_since = as.numeric(str_extract(host_since, "^[[:digit:]]{4}")),
         host_response_rate = as.numeric(str_extract(host_response_rate, "[[:digit:].]+")))
```

## Delete/Convert Missing Values

```{r}
colSums(is.na(df_listings))

avg_resonse_time <- tail(names(sort(table(df_listings$host_response_time))), 1) # Get most frequent value of response time

df_listings$host_response_time[is.na(df_listings$host_response_time)] <- avg_resonse_time # Fill na with most frequent value (average)
df_listings$security_deposit[is.na(df_listings$security_deposit)] <- 0 # Empty field for security deposit -> no deposit (=0)
df_listings$cleaning_fee[is.na(df_listings$cleaning_fee)] <- 0 # Empty field for cleaning fee -> no fee (=0)
        
df_listings <- df_listings %>% drop_na() # Delete remaining missing values
colSums(is.na(df_listings))
```

## Feature engineering
```{r}
netherlands = c("Netherlands|NL")

df_listings <- df_listings %>%
  mutate(host_location = str_detect(host_location, netherlands), # Host is dutch or not dutch
         latitude = as.factor(str_extract(latitude, "[[:digit:].]{4}")), # Factors for location (longitude/latitude)
         longitude = as.factor(str_extract(longitude, "[[:digit:].]{4}")),
         host_verifications = 1 + str_count(host_verifications, "', '"), # No. of verifications
         amenities = 1 + str_count(amenities, ","), # No. of amenities
         property_type = recode(property_type,"Townhouse" = "House", "Bungalow"="House", "Guesthouse"="House", "Tiny   house"="House", "Villa"="House","Aparthotel"="Hotel/Hostel", "Boutique hotel"="Hotel/Hostel","Hostel"="Hotel/Hostel", "Hotel"="Hotel/Hostel", "Barn"="Other", "Boat"="Other", "Bus"="Other","Cabin"="Other","Camper/RV"="Other","Campsite"="Other","Casa particular (Cuba)"="Other","Castle"="Other","Chalet"="Other","Cottage"="Other", "Dome house"="Other","Earth house"="Other","Farm stay"="Other", "Houseboat"="Other", "Island"="Other", "Lighthouse"="Other", "Yurt"="Other","Condominium"="Apartment", "Guest suite"="Apartment", "Loft"="Apartment", "Bed and breakfast"="Service", "Serviced apartment"="Service"),
         property_type = factor(property_type, levels = c("Apartment", "Hotel/Hostel", "House", "Service", "Other")), # Classify property type
         host_years = 2018 - host_since, # Years host has been on platform
         host_response_rate = as.factor(df_listings$host_response_rate == 100)) # Does host respond to every request or not?

df_listings <- select(df_listings, -c("host_since")) #Delete variables that are not needed anymore
```

Cleaned dataframe: df_listings!

# Model Building

## Linear or logistic regression

## Ensemble method

## Decision trees or k-nearest neighbours